Histo of ____

### 2017-07-13 histo_template.rmd
cleaned the histo_template

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("/home/khoo/Documents/uni_work/4_sem_1/7111/pracs/histo/week_")
# rename 's/test-this/REPLACESTRING/g' *
```

```{r image_loop2, results = 'asis'}
dickpics <- gtools::mixedsort(list.files("images/"))
for(i in 1:length(dickpics)){
  cat("### ", strsplit(dickpics[i], "\\.")[[1]][1], "\n", '\\includegraphics[width=\\linewidth,height=\\textheight,keepaspectratio]{{"', file.path("images", strsplit(dickpics[i], "\\.")[[1]][1]), '"}.PNG}', "\n", "\n", sep = "")
}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("~/Documents/histo-test/")
#setwd("/home/khoo/Documents/uni_work/4_sem_1/7111/pracs/histo/week_")
# rename 's/test-this/REPLACESTRING/g' *

### Requirements ###
# LaTeX engine with \usetheme{metropolis} (TeXlive-full?!)
# Directory called "images"
# ONLY image files in images that \includegraphics will allow for
# Pandoc/knitr (comes with RStudio by default)

### Notes ###
#    \includegraphics{{"../Current folder/1.This file"}.png}
# will not include the file name at the same time the quotations
# The extra curly brackets are to ensure we can choose it from a directory
# Below had to switch the ' and " around because LaTeX uses "
```

```{r image_loop2, results = 'asis'}
png_image_ext <- gtools::mixedsort(list.files("images/"))
png_image <- c()
image_ext <- c()
for(i in 1:length(png_image_ext)){
  png_image[i] <- strsplit(png_image_ext[i], "\\.")[[1]][1]  # removing the extension
  image_ext[i] <- strsplit(png_image_ext[i], "\\.")[[1]][2]  # keeping the extension

  cat("### ", png_image[i], "\n",  # name of the image
      "\\includegraphics[width=\\linewidth,height=\\textheight,keepaspectratio]{{",
      '"images/', png_image[i], '"}.', image_ext[i], "}", "\n", "\n", sep = "")
}
```

### 2017-07-13 histo_template_clean_leaves_extra_line.rmd
cleaned the histo_template

### Requirements ###
# LaTeX engine with \usetheme{metropolis} (TeXlive-full?!)
# Directory called "images"
# ONLY image files in images that \includegraphics will allow for
# Pandoc/knitr (comes with RStudio by default)
```

```{r image_loop2, results = 'asis'}
png_image_ext <- gtools::mixedsort(list.files("images/"))
png_image <- c()
for(i in 1:length(png_image_ext)){
  png_image[i] <- strsplit(png_image_ext[i], "\\.")[[1]][1]  # removing the extension

  cat("### ", png_image[i], "\n",  # name of the image
      "\\includegraphics[width=\\linewidth,height=\\textheight,keepaspectratio]{{",
      file.path("images", png_image_ext[i]), "}}", "\n", "\n", sep = "")
}
```

>>>>

### Requirements ###
# LaTeX engine with \usetheme{metropolis} (TeXlive-full?!)
# Directory called "images"
# ONLY image files in images that \includegraphics will allow for
# Pandoc/knitr (comes with RStudio by default)

### Notes ###
#    \includegraphics{{"../Current folder/1.This file"}.png}
# will not include the file name at the same time
```

```{r image_loop2, results = 'asis'}
png_image_ext <- gtools::mixedsort(list.files("images/"))
png_image <- c()
image_ext <- c()
for(i in 1:length(png_image_ext)){
  png_image[i] <- strsplit(png_image_ext[i], "\\.")[[1]][1]  # removing the extension
  image_ext[i] <- strsplit(png_image_ext[i], "\\.")[[1]][2]  # keeping the extension

  cat("### ", png_image[i], "\n",  # name of the image
      "\\includegraphics[width=\\linewidth,height=\\textheight,keepaspectratio]{{",
      file.path("images", png_image_ext[i]), "}.", image_ext[i], "}", "\n", "\n", sep = "")
}
```

### 2017-07-13 msk2.rmd
added clean histo template
cleaned the histo_template

>>>>

# Short case 1

> Michael Lee 24M back pain 4 years worse in the morning

Anatomical structures:

-  Tendons, ligaments, muscles
-  Nerves, spinal cord
-  Kidneys: stones/cyst
-  Repro stuff iff female

Questions to ask

-  PC: SOCRATES: have you had any bladder weakness (neuro question)?

> Pain gets better on exercise.

Types of back pain

| Type | Character | Time course | Radiation | NSAID response | Onset | Age |
| ------ |---------------  | ---------- | --------- | ------- |  ------ | ----- |
| Mechanical | Thinking muscular: diffuse/achey | Worse with movement PM AM | Lumbar to back of thigh | Moderate/good | Post trauma/gradual | Mid-late |
| Inflammation | Something pushing: stabbing | AM more likely than PM | To the butt | Really good | Insidious/gradual | 20s |
| Radicular | Sharp/stabbing | Worse with activity | Goes down the leg towards ankle and foot | Limited | Usually sudden | Any |
| Neuropathic | Burning | Constant, no association with activity | Towards ankle and foot | Limited | Insidious |
| Malignant | Deep gnawing contionuous ache | Constant, wakes up at night | Limited | Insidious |

What are the types of spondyloarthropathies (Rheumatoid factor negative)

-  Ankylosing spondylitis: $M>F$,
-  Psoriatic arthritis: nail pitting, sausage fingers
-  Reactive arthritis: after an infn (think UTIs, STIs), $M>F$
-  IBD associated: 
-  
-

Range of symptoms (don't forget extra-articular symptoms):

-  Oseopenia
-  LOTS of CVS issues

Natural Hx:

-  Inflamm of tendons (such as calcaneal tendon)
-  Oedema
-  Ossification
-  Fusion of spine => bamboo spine

Treatment:

-  Pain management: NSAIDs
-  Physiotherapy: also helps manage pain whilst preventing fusion

Effects:

-  Depression
-  Affect work: maybe think about re-skilling

# Short case 2

DDx for mono-articular pain:

-  Gout 
-  Septic arthropathies
-  Trauma
-  Osteoarthritis
-  Psoriatic arthritis
